Probabilistic Catalogs for Crowded Stellar Fields

### 2012-10-28 paper/ms.tex
New figure
Commented out pixel convolved PSF section

@@

\section{Pixel Convolved PSF}
{\bf Do people need to be schooled on this? I did...}
Consider a ``true image'' $f_0(x, y)$ with infinite resolution. We now model how
this image gives rise to the observed data. First, it is convolved with a
PSF $g(\delta_x, \delta_y)$ (assumed normalized to 1) to give the blurred image:
\begin{eqnarray}
f_{\rm{blurred}}(x, y) &=& \iint f_0(x-\delta_x, y-\delta_y)
g(\delta_x, \delta_y) \, d\delta_x \, d\delta_y \label{blur}
\end{eqnarray}
Then, we observe the blurred image with a certain pixellation. Consider a pixel.
The true flux $F$ within the pixel is:
\begin{eqnarray}
F &=& \iint_{\rm pixel} f_{\rm blurred}(x, y) \,dx'\,dy'\\
&=& \iint f_{\rm blurred}(x, y)\mathbbm{1}\left[(x,y) \in \textnormal{pixel}
\right] \,dx\,dy \label{pixel}
\end{eqnarray}
Now consider $F$ as a function of the central location $(x_c, y_c)$ of the
pixel.

>>>>

\begin{figure}
\begin{center}
\includegraphics[scale=0.45]{Figures/sex_inference.eps}
\end{center}
\caption{Inference of the luminosity function parameters using the $\sigma=0.5$
catalog from \sex.\label{fig:sex_inference}}
\end{figure}

@@

%\section{Pixel Convolved PSF}
%{\bf Do people need to be schooled on this? I did...}
%Consider a ``true image'' $f_0(x, y)$ with infinite resolution. We now model how
%this image gives rise to the observed data. First, it is convolved with a
%PSF $g(\delta_x, \delta_y)$ (assumed normalized to 1) to give the blurred image:
%\begin{eqnarray}
%f_{\rm{blurred}}(x, y) &=& \iint f_0(x-\delta_x, y-\delta_y)
%g(\delta_x, \delta_y) \, d\delta_x \, d\delta_y \label{blur}
%\end{eqnarray}
%Then, we observe the blurred image with a certain pixellation. Consider a pixel.
%The true flux $F$ within the pixel is:
%\begin{eqnarray}
%F &=& \iint_{\rm pixel} f_{\rm blurred}(x, y) \,dx'\,dy'\\
%&=& \iint f_{\rm blurred}(x, y)\mathbbm{1}\left[(x,y) \in \textnormal{pixel}
%\right] \,dx\,dy \label{pixel}
%\end{eqnarray}
%Now consider $F$ as a function of the central location $(x_c, y_c)$ of the
%pixel.
